The Rockerverse: Images, Packages, and Applications for Containerization with R

### 2020-01-18 manuscript.Rmd
Added Whole Tale description and journal reproducibility audit use case

@@

@@

@@

The ordering of authors following DN as first author is alphabetical. DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
NX wrote the section on \pkg{liftr}.
All authors approved the final version. This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

  - name: Craig Willis
    # https://github.com/craig-willis
      - 501 E. Daniel St.
      - \orcid{0000-0002-6148-7196}
    email: willis8@illinois.edu

@@

**Whole Tale** (https://wholetale.org) is a National Science Foundation (NSF) funded project\footnote{NSF Award OAC-1541450} developing a scalable, open-source, multi-user platform for reproducible research \citep{brinckman2019, chard2019a}. A central goal of the platform is to enable researchers to easily create and publish executable research objects\footnote{In Whole Tale a `tale` is a research object that contains metadata, data (by copy or reference), code, narrative, documentation, provenance, and information about the computational environment to support computational reproducibility} associated with published research \citep{chard2019b}. For R users, Whole Tale attempts to combine the strengths of the Rocker Project's curated Docker images with the Jupyter Project's `repo2docker`\footnote{See \href{https://repo2docker.readthedocs.io/}{https://repo2docker.readthedocs.io/}} component to simplify the customization of R-based environments for researchers with limited experience with either Docker or Git. Using Whole Tale, researchers can create and publish Rocker-based reproducible research objects to a growing number of repositories including DataONE member nodes, Zenodo and soon Dataverse. Additionally, Whole Tale supports automatic data citation and is working on capabilities for image preservation and provenance capture to improve the transparency of publish computational research artifacts \citep{mecum2018, mcphillips2019}.

@@

## Publication Reproducibility Audits

A recommendation of the recent National Academies' report on _Reproducibility and Replicability in Science_ is that journals "consider ways to ensure computational reproducibility for publications that make claims based on computations" \citep{NASEM2019}.  In fields such as Political Science and Economics, journals are increasingly adopting policies requiring authors to publish the code and data required to reproduce computational findings reported in published manuscripts, subject to independent verification \citep{Jacoby2017,Vilhuber2019,Alvarez2018,Christian2018,Eubank2016,King1995}. Problems with the computational environment, installation and availability of software dependencies are common. R is gaining popularity in these communities (in a sample of 105 replication packages published by the _American Journal of Political Science_ (AJPS) over 65% use R). Projects such as NSF Whole Tale use the Rocker Project community images with the goal of improving the reproducibility of published research artifacts and simplifying the publication and verification process for both authors and journals by reducing errors and time spent specifying the environment.

@@

The ordering of authors following DN as first author is alphabetical. DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about Containerization and Rocker.
RC \& EH contributed to the section on interfaces for Docker in R.
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
BM wrote the section on research compendia and made the project Binder-ready.
HN \& JN co-wrote the section on enterprise production environments (\pkg{googleComputeEngineR}, Google Cloud Run, Kubernetes).
KR wrote the section about \pkg{wholepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX wrote the section on \pkg{liftr}.
All authors approved the final version. This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

@@

DN is supported by the project Opening Reproducible Research ([o2r](https://www.uni-muenster.de/forschungaz/project/12343)) funded by the German Research Foundation (DFG) under project number [PE&nbsp;1632/17-1](https://gepris.dfg.de/gepris/projekt/415851837).
The funders had no role in data collection and analysis, decision to publish, or preparation of the manuscript. CW is supported by the Whole Tale projects (https://wholetale.org) funded by the US National Science Foundation (NSF) under award [OAC-1541450](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1541450).
